Predicting Water Treatment Plant Chemical Doses

### 2025-12-11 Presentation DSCI445.Rmd
Removed a slide of linear models section

# Performance

- Performed best with multiple interactions between Conductivity, Temp, and pH.

- Still not great predictions, many are overfit and underfit.

- Linear structure doesn't capture the relations in our predictors.

@@

@@

@@

# select LDA to take metrics of
qda_fit <- qda_fit2

@@

@@

>>>>

@@

- Experimented with predictor sets and found that pH and temperature (plus the associated lagged variables) were the main effective predictors.
- Turbidity and conductivity did not improve prediction.

LDA ACCURACY: 43.7%

@@

- Experimented with predictor sets and found that pH and temperature (plus the associated lagged variables) were the main effective predictors.
- Turbidity and conductivity did not improve prediction.

QDA ACCURACY: 35.7%

@@

# select QDA to take metrics of
qda_fit <- qda_fit2

@@

- Experimented with predictor sets and found that pH and temperature (plus the associated lagged variables) were the main effective predictors.
- Turbidity and conductivity did not improve prediction.

MULTINOMIAL ACCURACY: 46.3%

@@

- Experimented with predictor sets and found that pH and temperature (plus the associated lagged variables) were the main effective predictors.
- Turbidity and conductivity did not improve prediction.

RANDOM FOREST ACCURACY: 39.2%
